Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays

### 2015-02-16 draft.tex
Fix two typos
Incorporate some of Ulrik's comments

%% Draft Macros %%
\newcommand{\todo}[1]{{\color{red}\bf ToDo: #1}}
\newcommand{\danny}[1]{{\color{purple}#1}}
\newcommand{\fred}[1]{{\color{brown!85!black}#1}}
\newcommand{\nico}[1]{{\color{green!85!black}#1}}
\newcommand{\citeneeded}{{\color{red}\bf [cite needed]}}

@@

Our initial motivation for studying what we wish to call the
\emph{method of moments} is the determination of angular observables
in the rare decay FCNC-mediated decay $\bar{B}\to \bar{K}^*(\to
\bar{K}\pi)\ell^+\ell^-$. However, note that the method we
describe in the following is general, and it applies to arbitrary decay
or scattering processes. We find a previous work \cite{Dighe:1998vk}
that advocates this method chiefly for the determination of angular
observables in non-leptonic $B$ decays, but also mentions the
applicability to semileptonic decays. Our aim is to improve upon this previous
work by studying the uncertainties that are introduced by mismodelling
of the angular distribution, and by working out a recipe to determine
and unfold detector effects. Moreover, we show
that the method of moments has two major advantages over the usual
approach based on likelihood fits:
\begin{enumerate}
    \item Likelihood fits have convergence problems for a small number of
        events, and can require reparametrizations and/or approximations
        for a successful fit to the signal PDF, see e.g. \cite{Egede:1142152}.
        The method of moments has no such convergence problems.
    \item The results of likelihood fits suffer from systematic uncertainties
        and systematic bias (see e.g. \cite{Egede:1142152}), especially in but not limited
        to cases in which the PDFs do not faithfully model the underlying physics. We will
        show that the method of moments does not suffer a very particular type of
        mismodelling that arises from introducing a cutoff in a partial wave expansion.
    \item Using the method of moments, the joint probability distribution of the
        angular observables converges towards a multivariate Gaussian distribution.
        This allows an easy transfer of correlation information from the experiments to
        interested theorists.
\end{enumerate}

@@

Compared to the usual maximum-likelihood approach, we find for the method of moments:
\begin{enumerate}
  \item The angular observable ${S_i}$ can be determined
  independently of any other observable ${S_j}$. It is therefore
  much more robust to physics assumptions needed to define the full
  likelihood. In particular, this means one does not have to be
  specific regarding the form of new-physics contributions; in fact,
  one does not even need to be able to explicitly formulate the
  likelihood at all.
\item It is superior for a small number of samples $N$. Likelihood
  fits tend to be numerically unstable if lots of parameters need to
  be estimated from sparse data. This is more severe if the mode of
  the likelihood is near the boundary of the physically allowed
  region.\fred{Is there some LHCb note we could cite?} 
  For some of these decays of interest, there are only $\order{10}$ of events
  per bin on record.
\item The estimate is unbiased for any $N$. In contrast, the
  maximum-likelihood estimate has a bias of order
  $1/N$~\cite{Cox:1968}. In practice, one should keep in mind the
  bias-variance trade-off: it is a well known phenomenon that removing
  the bias usually leads to an increase in variance of the sampling
  distribution of the estimator and vice versa~\cite[sec. 7.3]{James:2006zz}. From a
  Bayesian decision-theory point of view, both contribute similarly to
  the expected loss associated with deciding on just one value of the
  unknown parameter. It is therefore highly questionable to reduce
  only the bias~\cite[sections 13.8,17.2]{jaynes:2003}. In fact, for
  the results discussed below in \refsec{numerics}, the likelihood
  fits --- if they converge --- produce uncertainties (10--15)\%
  smaller than those from the method of moments.
\item The approximate multivariate Gaussian distribution of $\vecest{S}$
  allows easier and more correct transfer of the information in the
  data to interested theorists for more accurate fits of
  standard-model and new-physics parameters \cite{Altmannshofer:2013foa,
    Descotes-Genon:2013wba,Bobeth:2013soa},
  or for more precise predictions of optimized observables; see e.g.,
  \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,
    Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf} for definitions
  of such optimized observables in $B\to K^*\ell^+\ell^-$ decays,
  \cite{Faller:2013dwa} for application to the decay $B\to
  \pi\pi\ell^-\bar\nu_\ell$, and \cite{Boeer:2014xx} for observables
  in $\Lambda_b\to\Lambda(\to N\pi)\ell^+\ell^-$). While the
  likelihood also approaches a multivariate Gaussian as $N \to
  \infty$, the two methods differ in their utility as input for
  theorists if $\widehat{\vec{S}}$ is not well
  inside the physical region. For example, suppose there are two
  angular observables that are constrained to a triangular region by
  phase-space or unitarity arguments as
  \begin{equation}
    \label{eq:constr-ex}
    |S_1| + S_2 \le 1, \, S_1 \in [-1,1],\, S_2 \in [0,1] \,.
  \end{equation}
  It may (and often does) happen in practice that $\widehat{\vec{S}}$
  is close or even outside the allowed region such that a significant
  part of the probability mass covers unphysical values. In a Bayesian
  fit, one would take $\mathcal{N}(\vecest{S} | \vec{S},
  \widehat{\Sigma})$ as the sampling distribution of the ``data'', and
  simply set a uniform prior on the triangle in the $\vec{S}$ plane
  defined by \refeq{constr-ex} to have a well defined problem. This
  could be trivially combined with other independent information in a
  global fit. Someone with a different physics model might have to
  consider a
  different physical region, and could incorporate it just as easily.\\

  For a likelihood fit, the constraint needs to be part of the
  analysis performed by the experimental collaboration, and the
  resulting likelihood as a function of $\vec{S}$ is distinctly not
  Gaussian.  For experimentalists, communicating such a result has
  proved to be challenging due to technical reasons (data formats,
  size etc.) and the fear that theorists misinterpret the many
  nuisance parameters (from control channels, detector calibrations
  etc.) that are also part of the likelihood. This leads to the
  undesirable situation that only the mode and standard errors
  are reported, and theorists often include the results as independent
  measurements with a Gaussian distribution and disregard the boundary
  problem as well as correlations altogether.

@@

In several interesting processes we might only have an approximate
result for $P$.  In this section, we focus on one particular class of
mismodelling of the signal PDF: the angular-momentum cutoff in partial
wave expansions. This mismodelling potentially affects a large number
of decays and scattering processes. For the sake of clarity we take
the interesting class of four-body decays $B\to P_1 P_2 \ell_1$
as an example\footnote{This includes the rare $b\to s$ mediated $B$ decay $B
  \to K\pi\ell^+\ell^-$, and the $V_{ub}$ suppressed decay $B\to
  \pi\pi\ell^+\bar\nu_\ell$. For both examples the PDF $P$ is known in
  the small-width approximation and when assuming a pure $P$-wave,
  resonant final state. An extension to $S-P$ interference has been
  studied for $B\to K\pi\ell^+\ell^-$
  \cite{Blake:2012mb,Becirevic:2011bp}, and for $\bar{B}\to
  \pi\pi\ell^-\bar\nu_\ell$ \cite{Faller:2013dwa}. For a first study
  of $S$, $P$
  and $D$ interference, see \cite{Das:2014sra}
}.\\

@@

For the selected class of decays, we can describe that problem as follows: The PDF $P$ has a fixed dependence on the dilepton
helicity angle $\theta_1$ and the azimuthal angle $\theta_3$. (See also \refapp{btokstarll} for details
on the angular distribution.) However, at the level of decay amplitudes the dimeson system can have an arbitrarily
large total angular momentum $j$; only its third component is restricted to $j_z = -1,0,+1$.
It is then usual to compute the angular distribution explicitly in terms of $\theta_1$ and $\theta_3$, but leave
the angular observables dependent on the remaining helicity angle $\theta_2$.
We advocate here that is a sensible procedure to perform an expansion in terms of Legendre polynomials $p_{j}^{(|m|)}$
with respect to the remaining angle $\theta_2$. Using the observables $S_k(\vec{\nu})$, $k=1,\dots,9$, with $\vec{\nu}=(q^2, k^2)$
and as defined in \refapp{partial-waves}, the expansion reads
\begin{equation}
    S_{k}(\vec{\nu},\cos\theta_2) \equiv \sum_{j} \frac{1}{n_{j,|m|}} S_{k,j}(\vec{\nu}) p_{j}^{(|m|)}(\cos\theta_2)\sin\theta_2\,,
\end{equation}
where the the normalization factor $n_{j,|m|}$ is defined in \refeq{legendre-scalar-product}. Within our
example we have (cf. also \refapp{btokstarll} and \cite{Lee:1992ih})
\begin{equation}
    |m| = \begin{cases}
        0\,, & k = 1,2,6\,,\\
        1\,, & k = 4,5,7,8\,,\\
        m\,, & k = 3,9
    \end{cases}\,.
\end{equation}
The angular observables $S_{k,j}$ defined as coefficients of this expansion in Legendre polynomials
have the merit of a well defined total angular momentum, and thus are physically discriminable.
As a consequence of the orthogonality of the Legendre polynomials, any mismodelling (or rather, lack of modelling of higher
partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section. To wit,
ignoring further (orthogonal) terms in the PDF cannot affect $\vec{S}$ nor its variance.\\

@@

We wish to emphasize, however, that detector acceptance effects systematically affect the expansion for any basis
of angular functions, including the one suggested in this section. The means to cope with this problem are discussed
in the following subsection.

@@

In what follows, we propose a systematic method to unfold all effects
of $\Ekernel$ through MC simulations and the method of moments
assuming that $\Ekernel$ is independent of the angular
observables, and that it is possible to expand $\Ekernel$ --- at
least formally --- in Legendre polymials.  For illustration, we
proceed with the explicit example of a uniangular\footnote{%
  The generalization of this section to multiangular PDFs is
  straighforward. It can be achieved by promoting $x$ to a vector,
  promoting the Legendre polynomials to products of independent
  polynomials or spherical harmonics, and promoting the indices
  $i,j,k,m$ to multi-indices.  } PDF with $x = \cos\theta$. Let us
define the PDF in terms of the Legendre polymials (i.e., $f_k(x)
\equiv P_k(x)$) and angular observables $\vec{S}$ as
\begin{equation}
    P\subt(\xt) \equiv P\subt(\xt | \vec{S}) = \sum_k S_k f_k(\xt),
  \end{equation}
where $k = 0, 1, \dots$ denotes an angular-momentum-like index associated with the observables.
Normalization of $P\subt$ is equivalent to choosing $S_0 = 1/2$. Requiring $P\subt(\xt) \ge 0 \,\forall \xt$
implies $|S_k| \leq 1/2$ for $k > 0$. More stringent relations between the
$S_k$ might hold, but are beyond the scope of this work. For later use, we define
\begin{equation}
  \label{eq:def-Sk}
  S^{(m)}_k \equiv
  \begin{cases}
    1/2 \delta_{k,0}, & m=0\\
    1/2 (\delta_{k,0} + \delta_{k,m}), & m>0 \,,
  \end{cases}
\end{equation}
and note that
\begin{equation}
    P^{(m)}(\xt) \equiv P(\xt | \vec{S}^{(m)})
\end{equation}
is a valid PDF. The dual basis of angular functions follows then from the normalization
and orthogonality of the Legendre polynomials, and one therefore has
\begin{equation}
    \tilde{f}_k(x) = \frac{2 k + 1}{2} f_k(x),\qquad \int_{-1}^{+1} \tilde{f}_k(x) f_l(x) \rmdx{x} = \delta_{k,l}\,.
\end{equation}
We now define the \emph{simulated raw} moments $\vec{Q}^{(m)}$ as
\begin{equation}
    Q_i^{(m)} \equiv \iint \tilde{f}_i(\xd) P^{(m)}(\xt) \Ekernel \rmdx{\xt} \rmdx{\xd},
\end{equation}
which are instrumental to our recipe. Monte Carlo estimators of these moments can be constructed from specifically crafted detector events $x_\text{d}^{(n,m)}$, $n = 1, \dots, N_\text{d}^{(m)}$, where
\begin{equation}
    x_\text{d}^{(n,m)} \sim P_E^{(m)}(\xd) \equiv \frac{1}{R^{(m)}} \int P^{(m)}(\xt) \Ekernel \rmdx{\xt}\,.
\end{equation}
In words, for each $m$ it is required to generate events from
a toy physical distribution $P^{(m)}$ in which $S_0 = S_m=1/2$ and all other
observables are set to zero, and to propagate these events through
a detector simulation. The normalization $R^{(m)}$ is chosen such
that $\int P_E^{(m)}(\xd) \rmdx{\xd} = 1$.  We emphasize that
$R^{(m)}$ can be estimated as $\est{R}^{(m)} = N_\text{d}^{(m)} /
N_\text{t}$, where $N_\text{t}$ corresponds to the number of
simulated true events.  The estimators then read
\begin{equation}
    \est{Q}_i^{(m)} \equiv \est{R}^{(m)} \frac{1}{N_\text{d}} \sum_n^{N_\text{d}} \tilde{f}_i(x_\text{d}^{(n,m)})
\end{equation}

@@

We note that $\vecest{S}$ as determined from \refeq{estS} does not fully correspond to $\vec{S}$
for arbitrary $\eps$. Taking again the decay $B\to K\ell^+\ell^-$
as an example, we have $\dim S = 3$. Assuming an expansion of the detector acceptance $\eps$
in terms of Legendre polynomial up to order $L$, we have to calculate the raw moments up
to $\dim \est{Q} = \dim \est{S} = \dim S + L$. The MC estimators of the corrected angular observables
then take the following structure:
\begin{equation}
    \lbrace \est{S}_k \rbrace = \lbrace \underbrace{\est{S}_0, \dots, \est{S}_{\dim S}}_\text{physical}, \underbrace{\est{S}_{\dim S + 1}, \dots, \est{S}_{\dim Q}}_\text{``superfluous''}\rbrace\,.
\end{equation}
The method is consistent as long as the MC estimators for the ``superfluous'' observables with indices $\dim S + 1$ to $\dim Q$
are compatible with zero. \footnote{This holds only for the physical model of uniangular decay distributions. For some decays, these superfluous observables
correspond to higher partial waves that have been suppressed in the physical model; see \refapp{btokstarll} for such a case.}
Since $L$ depends on the setup of the particle detector under consideration, it remains for
the experimental collaborations to determine the maximum order of such an expansion.\\

@@

We now study the performance of the proposed method. In order to do so, we simulate
individual events for two separate physical processes: one uni-angular, and one tri-angular decay
distribution. We repeats theses analysis for varying sample sizes, ranging from
$50$ to $500$ events. Our toy analysis base on SM predictions for angular observables
in the decays $B\to K\ell^+\ell^-$ and $B\to K^*(\to K\pi)\ell^+\ell^-$, respectively.
In order to faithfully investigate the performance of the method of moments, we repeats our
numerical studies for several bin sizes in the kinematic range $1\,\GeV^2 \leq q^2 \leq 6\,\GeV^2$,
as well as $15\,\GeV^2 \leq q^2 \leq q^2_\text{max}$. Here, the bin size is chosen either
as $1\,\GeV^2$ or $0.5\,\GeV^2$. This setup is meant to ensure that a wide spectrum of possible
values for the angular observables is investigated.\\

>>>>

%% Draft Macros %%
\newcommand{\todo}[1]{{\color{red}\bf ToDo: #1}}
\newcommand{\danny}[1]{{\color{purple}#1}}
\newcommand{\fred}[1]{{\color{brown!85!black}#1}}
\newcommand{\citeneeded}{{\color{red}\bf [cite needed]}}
\newcommand{\add}[1]{\textcolor{green!85!black}{#1}}
\newcommand{\del}[1]{\textcolor{red!85!black}{#1}}

@@

Our initial motivation for studying what we wish to call the
\emph{method of moments} is the determination of angular observables
in the rare decay FCNC-mediated decay $\bar{B}\to \bar{K}^*(\to
\bar{K}\pi)\ell^+\ell^-$. However, note that the method we
describe in the following is general, and it applies to arbitrary decay
or scattering processes. We find a previous work \cite{Dighe:1998vk}
that advocates this method chiefly for the determination of angular
observables in non-leptonic $B$ decays, but also mentions the
applicability to semileptonic decays. Our aim is to improve upon this previous
work by studying the uncertainties that are introduced by mismodelling
of the angular distribution, and by working out a recipe to determine
and unfold detector effects. Moreover, we show
that the method of moments has two major advantages over the usual
approach based on likelihood fits:
\begin{enumerate}
    \item \del{Likelihood fits have convergence problems for a small number of
        events, and can require reparametrizations and/or approximations
        for a successful fit to the signal PDF, see e.g. \cite{Egede:1142152}.
        The method of moments has no such convergence problems.
    }
    \item \add{Likelihood fits of problems, for which the underlying
        physical model is only partially known, may be delicate. Such cases can lead to
        overestimating the number of physical parameters, and consequently
        inhibit the convergence of the fits. (As an example, this type
        of problem occured in toy studies of the decay $B\to K^*(\to K\pi)\ell^+\ell^-$
        as reported in \cite{Egede:1142152}. It was subsequently solved
        when a missing symmetry relation between the angular observables
        was found and applied, thereby reducing the number of fit parameters.)
    }
    \item The results of likelihood fits suffer from systematic uncertainties
        and systematic bias \del{(see e.g. \cite{Egede:1142152})}, especially in but not limited
        to cases in which the PDFs do not faithfully model the underlying physics. We will
        show that the method of moments does not suffer a very particular type of
        mismodelling that arises from introducing a cutoff in a partial wave expansion.
    \item Using the method of moments, the joint probability distribution of the
        angular observables converges towards a multivariate Gaussian distribution.
        This allows an easy transfer of correlation information from the experiments to
        interested theorists.
\end{enumerate}

@@

Compared to the usual maximum-likelihood approach, we find for the method of moments:
\begin{enumerate}
  \item The angular observable ${S_i}$ can be determined
  independently of any other observable ${S_j}$. It is therefore
  much more robust to physics assumptions needed to define the full
  likelihood. In particular, this means one does not have to be
  specific regarding the form of new-physics contributions; in fact,
  one does not even need to be able to explicitly formulate the
  likelihood at all.
\item It is superior for a small number of samples $N$. Likelihood
  fits tend to be numerically unstable if lots of parameters need to
  be estimated from sparse data. This is more severe if the mode of
  the likelihood is near the boundary of the physically allowed
  region.\fred{Is there some LHCb note we could cite?}\danny{Ulrik suggests citing some
  statistical paper}
  For some of these decays of interest, there are only $\order{10}$--$\order{100}$ events
  per bin on record.\danny{What to cite? 1403.8004 only states total signal yield!}
\item The estimate is unbiased for any $N$. In contrast, the
  maximum-likelihood estimate has a bias of order
  $1/N$~\cite{Cox:1968}. In practice, one should keep in mind the
  bias-variance trade-off: it is a well known phenomenon that removing
  the bias usually leads to an increase in variance of the sampling
  distribution of the estimator and vice versa~\cite[sec. 7.3]{James:2006zz}. From a
  Bayesian decision-theory point of view, both contribute similarly to
  the expected loss associated with deciding on just one value of the
  unknown parameter. It is therefore highly questionable \add{to outright
  prefer the method of moments over likelihood fits, in order} to reduce
  only the bias~\cite[sections 13.8,17.2]{jaynes:2003}. In fact, for
  the results discussed below in \refsec{numerics}, the likelihood
  fits --- if they converge --- produce uncertainties (10--15)\%
  smaller than those from the method of moments.
\item The approximate multivariate Gaussian distribution of $\vecest{S}$
    allows easier and more \add{precise}\del{correct} transfer of the information in the
  data to interested theorists for more accurate fits of
  standard-model and new-physics parameters \cite{Altmannshofer:2013foa,
Descotes-Genon:2013wba,Beaujean:2013soa},
  or for more precise predictions of optimized observables; see e.g.,
  \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,
    Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf} for definitions
  of such optimized observables in $B\to K^*\ell^+\ell^-$ decays,
  \cite{Faller:2013dwa} for application to the decay $B\to
  \pi\pi\ell^-\bar\nu_\ell$, and \cite{Boeer:2014xx} for observables
  in $\Lambda_b\to\Lambda(\to N\pi)\ell^+\ell^-$). While the
  likelihood also approaches a multivariate Gaussian as $N \to
  \infty$, the two methods differ in their utility as input for
  theorists if $\widehat{\vec{S}}$ is not well
  inside the physical region. For example, suppose there are two
  angular observables that are constrained to a triangular region by
  phase-space or unitarity arguments as
  \begin{equation}
    \label{eq:constr-ex}
    |S_1| + S_2 \le 1, \, S_1 \in [-1,1],\, S_2 \in [0,1] \,.
  \end{equation}
  It may (and often does) happen in practice that $\widehat{\vec{S}}$
  is close or even outside the allowed region such that a significant
  part of the probability mass covers unphysical values. In a Bayesian
  fit, one would take $\mathcal{N}(\vecest{S} | \vec{S},
  \widehat{\Sigma})$ as the sampling distribution of the ``data'', and
  simply set a uniform prior on the triangle in the $\vec{S}$ plane
  defined by \refeq{constr-ex} to have a well defined problem. This
  could be trivially combined with other independent information in a
  global fit. Someone with a different physics model might have to
  consider a
  different physical region, and could incorporate it just as easily.\\

  For a likelihood fit, the constraint needs to be part of the
  analysis performed by the experimental collaboration, and the
  resulting likelihood as a function of $\vec{S}$ is distinctly not
  Gaussian.  For experimentalists, communicating such a result has
  proved to be challenging due to technical reasons (data formats,
  size etc.) and the fear that theorists misinterpret the many
  nuisance parameters (from control channels, detector calibrations
  etc.) that are also part of the likelihood.
  \danny{Ulrik: Seems an odd comment to put in a paper.}
  This leads to the
  undesirable situation that only the mode and standard errors
  are reported, and theorists often include the results as independent
  measurements with a Gaussian distribution and disregard the boundary
  problem as well as correlations altogether.

@@

In several interesting processes we might only have an approximate
result for $P$.  In this section, we focus on one particular class of
mismodelling of the signal PDF: the angular-momentum cutoff in partial
wave expansions. This mismodelling potentially affects a large number
of decays and scattering processes. For the sake of clarity we take
the interesting class of four-body decays $B\to P_1 P_2 \ell_1 \ell_2$
as an example\footnote{This includes the rare $b\to s$ mediated $B$ decay $B
  \to K\pi\ell^+\ell^-$, and the $V_{ub}$ suppressed decay $B\to
  \pi\pi\ell^+\bar\nu_\ell$. For both examples the PDF $P$ is known in
  the small-width approximation and when assuming a pure $P$-wave,
  resonant final state. An extension to $S-P$ interference has been
  studied for $B\to K\pi\ell^+\ell^-$
  \cite{Blake:2012mb,Becirevic:2011bp}, and for $\bar{B}\to
  \pi\pi\ell^-\bar\nu_\ell$ \cite{Faller:2013dwa}. For a first study
  of $S$, $P$
  and $D$ interference, see \cite{Das:2014sra}
}.\\

@@

For the selected class of decays, we can describe that problem as follows: The PDF $P$ has a fixed dependence on the dilepton
helicity angle $\theta_1$ and the azimuthal angle $\theta_3$. (See also \refapp{btokstarll} for details
on the angular distribution.) However, at the level of decay amplitudes the dimeson system can have an arbitrarily
large total angular momentum $j$; only its third component is restricted to $j_z = -1,0,+1$.
It is then \add{convenient}\del{usual} to compute the angular distribution explicitly in terms of $\theta_1$ and $\theta_3$, but leave
the angular observables dependent on the remaining helicity angle $\theta_2$.
We advocate here that is a sensible procedure to perform an expansion in terms of Legendre polynomials $p_{l}^{(|m|)}$
with respect to the remaining angle $\theta_2$. \add{Here, the angular momentum-like indices $l$ and $m$ follows from the usual
rules for addition of the angular momenta $j$ and $\tilde{j}$ of the partial wave expansion of the underlying
amplitude and its complex conjugate: $j - \tilde{j} \leq l \leq j + \tilde{j}$, and $m = j_z + \tilde{j}_z$.}
Using the observables $S_k(\vec{\nu})$, $k=1,\dots,9$, with $\vec{\nu}=(q^2, k^2)$
and as defined in \refapp{partial-waves}, the expansion reads
\begin{equation}
    S_{k}(\vec{\nu},\cos\theta_2) \equiv \sum_{j} \frac{1}{n_{l,|m|}} S_{k,l}(\vec{\nu}) p_{l}^{(|m|)}(\cos\theta_2)\sin\theta_2\,,
\end{equation}
where the the normalization factor $n_{l,|m|}$ is defined in \refeq{legendre-scalar-product}. Within our
example we have (cf. also \refapp{btokstarll} and \cite{Lee:1992ih})
\begin{equation}
    |m| = \begin{cases}
        0\,, & k = 1,2,6\,,\\
        1\,, & k = 4,5,7,8\,,\\
        2\,, & k = 3,9
    \end{cases}\,.
\end{equation}
The angular observables $S_{k,j}$ defined as coefficients of this expansion in Legendre polynomials
have the merit of a well defined total angular momentum, and thus are physically discriminable.
As a consequence of the orthogonality of the Legendre polynomials, any mismodelling (or rather, lack of modelling of higher
partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section. \del{To wit}\add{That is to say},
ignoring further (orthogonal) terms in the PDF cannot affect $\vec{S}$ nor its variance.\\

@@

We wish to emphasize, however, that detector acceptance effects systematically affect the expansion for any basis
of angular functions, including the one suggested in this section.
\add{Nevertheless, the expansion in terms of Legendre polynomials provides means to cope with these effects,
as we discuss in the following subsection.}
\del{The means to cope with this problem are discussed
in the following subsection.}

@@

In what follows, we propose a systematic method to unfold all effects
of $\Ekernel$ through MC simulations and the method of moments.
\add{In this process, we use that fact} that $\Ekernel$ is independent of the angular
observables, and that it is possible to expand $\Ekernel$ --- at
least formally --- in Legendre polymials.  For illustration, we
proceed with the explicit example of a uniangular\footnote{%
  The generalization of this section to multiangular PDFs is
  straighforward. It can be achieved by promoting $x$ to a vector,
  promoting the Legendre polynomials to products of independent
  polynomials or spherical harmonics, and promoting the indices
  $i,j,k,m$ to multi-indices.  } PDF with $x = \cos\theta$. Let us
define the PDF in terms of the Legendre polymials (i.e., $f_k(x)
\equiv P_k(x)$) and angular observables $\vec{S}$ as
\begin{equation}
    P\subt(\xt) \equiv P\subt(\xt | \vec{S}) = \sum_k S_k f_k(\xt),
  \end{equation}
where $k = 0, 1, \dots$ denotes an angular-momentum-like index associated with the observables.
Normalization of $P\subt$ is equivalent to choosing $S_0 = 1/2$. Requiring $P\subt(\xt) \ge 0 \,\forall \xt$
implies $|S_k| \leq 1/2$ for $k > 0$. More stringent relations between the
$S_k$ might hold, but are beyond the scope of this work. For later use, we define
\begin{equation}
  \label{eq:def-Sk}
  S^{(m)}_k \equiv
  \begin{cases}
    1/2 \delta_{k,0}, & m=0\\
    1/2 (\delta_{k,0} + \delta_{k,m}), & m>0 \,,
  \end{cases}
\end{equation}
and note that
\begin{equation}
    P^{(m)}(\xt) \equiv P(\xt | \vec{S}^{(m)})
\end{equation}
is a valid PDF. The dual basis of angular functions follows then from the normalization
and orthogonality of the Legendre polynomials, and one therefore has
\begin{equation}
    \tilde{f}_k(x) = \frac{2 k + 1}{2} f_k(x),\qquad \int_{-1}^{+1} \tilde{f}_k(x) f_l(x) \rmdx{x} = \delta_{k,l}\,.
\end{equation}
We now define the \emph{simulated raw} moments $\vec{Q}^{(m)}$ as
\begin{equation}
    Q_i^{(m)} \equiv \iint \tilde{f}_i(\xd) P^{(m)}(\xt) \Ekernel \rmdx{\xt} \rmdx{\xd},
\end{equation}
which are instrumental to our recipe. Monte Carlo estimators of these moments can be constructed from specifically crafted detector events $x_\text{d}^{(n,m)}$, $n = 1, \dots, N_\text{d}^{(m)}$, where
\begin{equation}
    x_\text{d}^{(n,m)} \sim P_E^{(m)}(\xd) \equiv \frac{1}{R^{(m)}} \int P^{(m)}(\xt) \Ekernel \rmdx{\xt}\,.
\end{equation}
In words, for each $m$ it is required to generate events from
a toy physical distribution $P^{(m)}$ in which $S_0 = S_m=1/2$ and all other
observables are set to zero, and to propagate these events through
a detector simulation. The normalization $R^{(m)}$ is chosen such
that $\int P_E^{(m)}(\xd) \rmdx{\xd} = 1$.  We emphasize that
$R^{(m)}$ can be estimated as $\est{R}^{(m)} = N_\text{d}^{(m)} /
N_\text{t}$, where $N_\text{t}$ corresponds to the number of
simulated true events.  The estimators then read
\begin{equation}
    \est{Q}_i^{(m)} \equiv \est{R}^{(m)} \frac{1}{N_\text{d}} \sum_n^{N_\text{d}} \tilde{f}_i(x_\text{d}^{(n,m)})
\end{equation}

@@

We note that $\vecest{S}$ as determined from \refeq{estS} does not fully correspond to $\vec{S}$
for arbitrary $\eps$. Taking again the decay $B\to K\ell^+\ell^-$
as an example, \del{we have} \add{there are exactly three physical angular observables:} $\dim S = 3$.
Assuming an expansion of the detector acceptance $\eps$
in terms of Legendre polynomial up to order $L$, we have to calculate the raw moments up
to $\dim \est{Q} = \dim \est{S} = \dim S + L$. The MC estimators of the corrected angular observables
then take the following structure:
\begin{equation}
    \vecest{S} = ( \underbrace{\est{S}_0, \dots, \est{S}_{\dim S}}_\text{physical}, \underbrace{\est{S}_{\dim S + 1}, \dots, \est{S}_{\dim Q}}_\text{``superfluous''})\,.
\end{equation}
The method is consistent as long as the MC estimators for the ``superfluous'' observables with indices $\dim S + 1$ to $\dim Q$
are compatible with zero. \footnote{This holds only for the physical model of uniangular decay distributions. For some decays, these superfluous observables
correspond to higher partial waves that have been suppressed in the physical model; see \refapp{btokstarll} for such a case.}
Since $L$ depends on the setup of the particle detector under consideration, it remains for
the experimental collaborations to determine the maximum order of such an expansion.
\add{We propose to do this by \dots}\\

@@

We now study the performance of the proposed method. In order to do so, we simulate
individual events for two separate physical processes: one uni-angular, and one tri-angular decay
distribution. We repeats theses analysis for varying sample sizes, ranging from
$50$ to $500$ events. Our toy analyses base on SM predictions for angular observables
in the decays $B\to K\ell^+\ell^-$ and $B\to K^*(\to K\pi)\ell^+\ell^-$, respectively.
In order to faithfully investigate the performance of the method of moments, we repeats our
numerical studies for several bins in the kinematic range $1\,\GeV^2 \leq q^2 \leq 6\,\GeV^2$,
as well as $15\,\GeV^2 \leq q^2 \leq q^2_\text{max}$. Here, the bin width is chosen either
as $1\,\GeV^2$ or $0.5\,\GeV^2$. This setup is meant to ensure that a wide spectrum of possible
values for the angular observables is investigated.\\

Our findings can be summarized as follows:
\begin{itemize}
    \item In all studied cases we observed not a single bias in the distribution of the $\mathrm{pull}$
        of any observables $S_i$,
        \begin{equation}
            \mathrm{pull_i} \equiv \frac{\est{S}_i - S_i}{\est{\sigma}_{i}}\,.
        \end{equation}
        Here $S_i$ refers to the true (input) value for the angular observables, $\est{S}_i$ refers to the
        mean of the pseudo measurement via the MC estimate, and $\est{\sigma}_{i} \equiv \est{\Sigma_{ii}}^{1/2}$
        refers to an estimator of the standard deviation of the pseudo measurement. All pull distributions
        obtained in our studies can be successfully
        fitted to a gaussian distribution. Due to the large number of studied distributions, we have
        to restrict ourselved to a subset. In our opinion the pull distributions for the observables
        $S_5 \simeq 27\%$ and $S_7 \simeq 2\%$, which are obtained from SM-like $B\to K^*\ell^+\ell^-$
        decays, are good examples. We show their respective pull distributions for $2\cdot 10^5$ toy studies
        of $200$ events per study in \reffig{pulls}.
    \item We study the MC estimate for the absolute uncertainty $\est{\sigma_i(N)}$ with respect to the angular observable $S_i$
        as a function of the number of simulated events $N$. As expected for a multivariate gaussian
        distribution, we find that the absolute uncertainty is well fitted by
        \begin{equation}
            \label{eq:unc-on-mean}
            \est{\sigma_i(N)} = \frac{\sigma_i}{\sqrt{N}}
        \end{equation}
        with $\sigma_i(1) = \order{1}$, regardless of the absolute size of $S_k$. The latter can best be shown
        for the example of uncertainties of two observables. Taking again $S_5$ ($\simeq 27\%$) and $S_7$ ($\simeq 2\%$)
        for SM-like $B\to K^*\ell^+\ell^-$ decays, we show the absolute uncertainty in \reffig{errors}.
        We find that the the method of moments yields uncertainties on $\vec{S}$ that are roughly
        $10\%$ -- $15\%$ larger than those obtained from maximum-likelihood fits and for the same
        number of events \danny{[cite!]}. However, we wish to note that said fits only produce a limited
        subset of the angular observables, and the statistical error of the fit is expected to increase
        with the number of fit parameters until their errors saturate the statistical errors of the method-of-moments
        estimators \cite[sec. 8]{Cowan:1998ji}.
%    \item For all toy studies, we produce plots of their skewness and their kurtosis as functions of
%        $N$. We find in all cases that the mean skewness and kurtosis converge towards zero.
%        \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of the number of simulated events $N$.}
\end{itemize}
All results of our toy studies, as summarised above, show consistently that the joint distribution of the angular
observables converges rapidly towards a multivariate Gaussian distribution. We therefore propose to describe the
resulting distribution as a multivariate Gauss when skewness and kurtosis fall below a given threshold.
The precise target threshold for skewness and kurtosis are subject to the details of the underlying physical analysis, and reside therefore outside the scope of this work.
